---
title: "MUSA6310_HW03"
author: "scurry"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: TRUE
    theme: united
    number_sections: FALSE
    toc_float: TRUE
    toc_depth: 2
    code_folding: hide
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(warning = FALSE, message = FALSE)
options(tigris_use_cache = TRUE,
        width = 50)
setwd("C:/LocalDocuments/GitHub/MUSA6310_HW03")

library(dplyr)
library(ggplot2)
library(kableExtra)
library(knitr)
library(scales)
library(sf)
library(tidycensus)
library(tigris)

# msa_mhi_22_cnt <- msa_mhi_22 %>%
#   arrange(desc(popE)) %>%
#   select(NAME, mhiE) %>%
#   rename("Metropolitan Statistical Area" = "NAME") %>%
#   mutate("Median Household Income" = scales::dollar(mhiE)) %>%
#   select(-mhiE) %>%
#   st_drop_geometry() %>%
#   head(8)
# 
# msa_mhi_22_cnt <- msa_mhi_22_cnt %>%
#   mutate(ID = c(1:8), .before = "Metropolitan Statistical Area")

```

## Graph One
```{r g1_data, message=FALSE, warning=FALSE, include=FALSE}

msa_mhi_22 <- get_acs(geography = "metropolitan statistical area/micropolitan statistical area",
                     year = 2022, 
                     variables = c(pop = "B01003_001", mhi = "B19013_001"),#median household income
                     geometry = TRUE,
                     output = "wide"
) 

phl_mhi_22 <- msa_mhi_22 %>%
  filter(GEOID == 37980)

```

```{r g1_graph, echo=FALSE, message=FALSE, warning=FALSE}

ggplot() +
  geom_histogram(data = msa_mhi_22, aes(x = mhiE), fill = "darkolivegreen4", color = "darkolivegreen") +
  scale_x_continuous(labels = scales::label_dollar()) +
  geom_vline(data = phl_mhi_22, aes(xintercept = mhiE), color = "goldenrod", linetype = "dashed",
             size = 1) +
  geom_text(data = phl_mhi_22, aes(x = mhiE + 3000, y = 100, label = "Philadelphia MSA"),
            color = "goldenrod", angle = 90) +
  labs(title = "DRAFT ONE: 2022 Median Household Income",
       subtitle = "US Metropolitan Statistical Areas",
       x = "Median Household Income",
       y = " ",
#       fill = "Percentage of Philadelphia MHI",
       caption = "Source: 2022 ACS, U.S. Census Bureau") +
  theme_minimal()

ggplot() +
  geom_histogram(data = msa_mhi_22, aes(x = mhiE), bins = 10, fill = "darkolivegreen4", color = "darkolivegreen") +
  scale_x_continuous(labels = scales::label_dollar()) +
  geom_vline(data = phl_mhi_22, aes(xintercept = mhiE), color = "goldenrod", linetype = "dashed",
             size = 1) +
  geom_text(data = phl_mhi_22, aes(x = mhiE + 3000, y = 300, label = "The Philadelphia MSA's MHI \n in 2022 was $85,555"),
            color = "goldenrod", hjust = 0) +
  labs(title = "DRAFT TWO: 2022 Median Household Income",
       subtitle = "US Metropolitan Statistical Areas",
       x = "Median Household Income",
       y = "Number of MSA's",
       caption = "Source: 2022 ACS, U.S. Census Bureau") +
  theme_minimal()

ggplot() +
  geom_histogram(data = msa_mhi_22, aes(x = mhiE), breaks = c(0, 20000, 40000, 60000, 80000, 100000, 120000, 140000, 160000), fill = "darkolivegreen4", color = "darkolivegreen") +
  scale_x_continuous(labels = scales::label_dollar(), breaks = seq(0, 160000, 20000)) +
  geom_vline(data = phl_mhi_22, aes(xintercept = mhiE), color = "goldenrod", linetype = "dashed",
             size = 1) +
  geom_text(data = phl_mhi_22, aes(x = mhiE + 3000, y = 300, label = "The Philadelphia MSA's MHI \n in 2022 was $85,555"),
            color = "goldenrod", hjust = 0) +
  labs(title = "FINAL: 2022 Median Household Income",
       subtitle = "US Metropolitan Statistical Areas",
       x = "Median Household Income",
       y = "Number of MSA's",
       caption = "Source: 2022 ACS, U.S. Census Bureau") +
  theme_minimal()

```

The first histogram is a pretty run of the mill export from ggplot with very little manipulation to the settings. Comments I received in class centered on asking "so what?" about what they were supposed to learn. I had wanted the graph to show that Philadelphia (the city I was about to discuss in my Assignment 1 article) was in a higher percentile of national MSA MHI than folks might assume. With an unlabeled y axis and a lot of x axis bins, there are too many questions raised about the other data points. Draft Two attempted to remedy this by lessening the number of bins and adjusting labels to be more clear. However, the x axis tick marks and the bins still don't align, making it unclear how many MSA's fall within what range of MHI. This is resolved at the final stage. The ink to data ratio is perhaps still not right, and the "so what?" of the graph is still weak. I no longer plan to use this exact graph in my final article - I think that the best way to share information in my article about income vs cost of living is with a graph that shows more nuanced data.

## Graph Two

```{r g2_data, message=FALSE, warning=FALSE, include=FALSE}

ct_size_20 <- get_acs(geography = "tract",
                      state = "MD",
                      year = 2020, 
                     variables = c(pop = "B01003_001"),
                     geometry = TRUE,
                     output = "wide"
) %>%
  mutate(area_meters = st_area(geometry))

ct_size_20$area_meters <- as.vector(ct_size_20$area_meters)

```

```{r g2_graph, echo=FALSE, message=FALSE, warning=FALSE}

ggplot() +
  geom_point(data = ct_size_20, aes(x = popE, y = area_meters)) +
  labs(title = "DRAFT ONE: 2020 Census Tract Area vs Population Size",
       subtitle = "Maryland",
       x = "Population",
       y = "Area in Meters^2",
       caption = "Source: 2020 ACS, U.S. Census Bureau")

ggplot() +
  geom_point(data = ct_size_20, aes(x = popE, y = area_meters), 
             color = if_else(ct_size_20$GEOID == "24019970900" | 
                               ct_size_20$GEOID == "24033980000" |
                               ct_size_20$GEOID == "24033802405", "red", "gray35"), 
             alpha = 0.5) +
  scale_x_continuous(labels = scales::label_comma()) +
  scale_y_continuous(labels = scales::label_comma()) +
  labs(title = "DRAFT TWO: 2020 Census Tract Area vs Population Size",
       subtitle = "Maryland",
       x = "Population",
       y = "Area in Meters^2",
       caption = "Source: 2020 ACS, U.S. Census Bureau") +
  theme_minimal()

ggplot() +
  annotate(geom = "rect", xmin = 1200, xmax = 8000, ymin = 0, ymax = 700000000, fill = "goldenrod", alpha = 0.15) +
  geom_point(data = ct_size_20, aes(x = popE, y = area_meters), 
             color = if_else(ct_size_20$GEOID == "24019970900" | 
                               ct_size_20$GEOID == "24033980000" |
                               ct_size_20$GEOID == "24033802405", "red", "gray35"), 
             alpha = 0.5) +
  scale_x_continuous(labels = scales::label_comma()) +
  scale_y_continuous(labels = scales::label_comma(scale = 0.000001, suffix = "M")) +
  annotate(geom = "text", x = 1000, y = 570000000,
           label = "a CT in Dorchester County", hjust = 0, color = "red") +
  annotate(geom = "text", x = 9000, y = 50000000,
           label = "a CT in Prince George's County", hjust = 0, color = "red") +
  annotate(geom = "text", x = 3600, y = 400000000,
           label = "a CT where the Census Bureau \nis located", hjust = 0, color = "red") +
  labs(title = "FINAL: 2020 Census Tract Area vs Population Size",
       subtitle = "Maryland",
       x = "Population",
       y = "Area in Square Meters",
       caption = "Source: 2020 ACS, U.S. Census Bureau") +
  theme_minimal()

```

The census bureau defines a census tract as a "small, relatively permanent statistical subdivision of a county. Census tracts average about 4,000 inhabitants (with a minimum population of 1,200 and a maximum of 8,000)." The United States Census Bureau is located in Hillcrest Heights, Maryland and this graph aims to take a look at how good the Bureau is at following its own rules in its home state. 



## Graph Three
